---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rasterio.py

<!-- badges: start -->
<!-- badges: end -->

The goal of rasterio.py is to provide an R interface to rasterio. 

rasterio is a Python package that provides low-level facilities to the [GDAL](https://www.gdal.org/), much like
the R [rgdal](https://CRAN.r-project.or/package=rgdal) did in the past. The Python bindings have always been closer and more complete to the spirit of the GDAL library itself than R, but rasterio itself is a modernization of the original Python support for GDAL. 

R does not have a comprehensive interface to the GDAL C++ library yet, so this package provides a showcase of what is possible. The facilities via Python are fine! The only real disadvantage is the dependency on Python, there's no obvious performance reason to avoid rasterio however. 

## Installation

You can install the development version of rasterio.py like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rasterio.py)
## basic example code
file <- rgba_tif()  ## just the path to the RGBA.byte.tif of rasterio canon
dataset <- open.py(file)

dataset$bounds
dataset$transform
```

rasterio.py has some R helper functions for these Python reticulate objects. 

plot, extent, more to come ...

WIP

```{r cars}
plot(dataset)

extent.py(dataset)

(warped <- warp.py(dataset$files[1], extent = c(-1, 1, -1, 1) * 1e5, dimension = c(512, 768), projection = "+proj=aeqd +lon_0=-77.6 +lat_0=24.5", resample = "cubic"))

plot(warped)
```


We can of course read from the COG!!  (but, overview handling isn't great yet so we're keeping examples close)

```{r cog-wonders, eval=FALSE, include =FALSE}
gebco <- "/vsicurl/https://public.services.aad.gov.au/datasets/science/GEBCO_2019_GEOTIFF/GEBCO_2019.tif"

dem <- open.py(gebco)
plot(dem)

dem <- warp.py(gebco, extent = c(130, 170, -65, -35), dimension = c(720, 360), projection = "OGC:CRS84")
plot(dem)
```
